
% Created 2017-11-13 Mon 14:23
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\tolerance=1000

\begin{document}

\textbf{Dave Hyde} at the \textit{South Florida Sun-Sentinel} says that the big three have to get better.  He concentrates on personnel.  I'm saying Gase has to be a better HC.

* Want to know why the members of the team weren't pointing the thunb as musch this year.  Count the number of times Adam Gase did it.  LAck of accountablility.
* Going from tough to wasy is a lot better than going from easy to tough.  Gase has a tough road ahead.  Will having new assistants help?

* Lack of discipline - 31st in penalties

* Quotes from earlier in the season from Gase about how some members of the team weren't working hard enough.
** Yeah, they got paid
** Yeah, they got comfortable


http://www.sun-sentinel.com/sports/dave-hyde-blog/fl-sp-hyde5-belichick-dolphins-20180202-story.html

One year it was assistant coaches. We talked about how with success the assistants become friends with the players.

"I said how [Dallas running backs coach] Joe Brodsky loved Emmitt Smith so much he quit pushing him. He'd get all over the backup. I'd say, 'Joe, you're not paying attention to the guy we need on Sunday.' He said, 'He'll be fine, he's a veteran.'

"I got mad at him, and that's what I told Belichick. 'You've got to be the hammer when you've had success.' The assistant coaches aren't going to be it anymore. It's up to you to be the [jerk]."

Jimmy laughed. "Bill's been very good at that."



  \end{document}
