\documentclass[11pt]{article}
\pagestyle{empty}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage[labelfont=bf]{caption}
\usepackage{sidecap}
\usepackage{xcolor}
\usepackage{mdframed}
\usepackage{chemist}
\usepackage{xspace}

\usepackage[colorlinks = true,
linkcolor = blue,
urlcolor  = blue,
citecolor = blue,
anchorcolor = blue]{hyperref}
\tolerance=1000

\newenvironment{mybox}{\begin{mdframed}\vspace{-14pt}}{\end{mdframed}}
\renewcommand{\familydefault}{cmss}
\renewcommand{\thefigure}{8.\arabic{figure}}
\renewcommand{\thetable}{8.\arabic{table}}
\addtolength{\oddsidemargin}{-.875in}
\addtolength{\evensidemargin}{-.875in}
\addtolength{\textwidth}{1.75in}

\addtolength{\topmargin}{-.875in}
\addtolength{\textheight}{1.75in}

% \newcommand{\trsem}[1]{\textbf{\textcolor{blue}{\colorbox{yellow}{#1}}}}
\newcommand{\trsem}[1]{\textbf{\textcolor{blue}{#1}}}
\newcommand{\supe}[1]{\textsuperscript{#1}}
\newcommand{\subs}[1]{\textsubscript{#1}}
\newcommand{\PO}{P\textsubscript{O2}\xspace}
\newcommand{\PAO}{P\textsubscript{A,O2}\xspace}
\newcommand{\PaO}{P\textsubscript{a,O2}\xspace}
\newcommand{\Ox}{O\textsubscript{2}\xspace}
\newcommand{\PCO}{P\textsubscript{CO2}\xspace}
\newcommand{\PACO}{P\textsubscript{A,CO2}\xspace}
\newcommand{\PaCO}{P\textsubscript{a,CO2}\xspace}
\newcommand{\CO}{CO\textsubscript{2}\xspace}
\newcommand{\Ca}{Ca\textsuperscript{+2}\xspace}
\newcommand{\nl}{\ \\}

\def\labelenumi{\Alph{enumi}.}
\def\labelenumii{\arabic{enumii}.}
\def\labelenumiii{\alph{enumiii}.}
\def\labelenumiv{\roman{enumiv}.}

\begin{document}
\subsection*{Defense}

\begin{enumerate}
\item The Bears defense was excellent, as usual.  They stopped the run and got pressure on Joe Flacco.
\item The Broncos were trying to get the ball out fast to prevent the Bears pass rush from getting to them.  They had limited success, especially early.  They did a good job of mixing the run and pass.
\item The Broncos occasionally had success running right at Khalil Mack.  We'll probably see more of that as the season wears on.  Phillip Lindsay had a good game running the ball.
\item The Broncos also had some success throwing underneath and running after the catch, especially Emmanuel Sanders.  On a related note, the Bears could have tackled better.  Roquon Smith especially seemed to hesitate against receivers in the open field.
\item It looked like the Bears rotated in quite a few players this game in an effort to rest their players at the high altitude, as well.  Aaron Lynch and Isaiah Irving got playing time.
\item Despite doing what they could to limit it, the Bears defense really looked worn down in the fourth quarter.
\item Perhaps on a related note, the Bears missed some big tackles down the stretch.
\end{enumerate}

\subsection*{Offense}

  \begin{enumerate}
  \item The Bears came out running and promptly got stuffed.  They stuck with it however and did find some success with both that and the short passing game.  They were able to sustain some long drives in the first half which allowed the Bears defense to rest in the thin Denver air.  The Broncos did not choose to load the box to stop the run.
  \item They were also trying to wear the Broncos defense down.  The didn't, though, as far as I could tell.
  \item Tarik Cohen and David Montgomery did a good job of making yards on their own.  Cohen's quickness makes him tough to bring down.  Montgomery had both patience and vision and he found some cracks and slipped through.
  \item Trubisky really still didn't have a good game.  Like last week, his accuracy was off.  The Broncos coverage was generally pretty good and Bears receivers had a hard time fighting them off for the ball. Chris Harris in particular did a nice job of covering Allen Robinson this game.
  \item Ted Larsen reported as eligible for the pass late in the third quarter?  Really?
  \end{enumerate}

  \subsection*{Miscellaneous}

  \begin{enumerate}
  \item Dick Stockton and Mark Schlereth were you announcers.  I usually like Schlereth because he provide some insight into offensive line play that you often don't get from other analysts.  But today I thought his enthusiasm might have been a little overdone at times.
  \item  Special Teams
    \begin{enumerate}
    \item Eddie Pineiro made two field goals in the first half, one from 52 yards.  He was the Bears offensive output in the first half.
    \item The Broncos did a good job of playing field position and the Bears started from inside their own 20 yard line quite a bit.
  \end{enumerate}
  \item Drops didn't have much to do with the outcome.
  \item Penalties
    \begin{enumerate}
    \item Broncos left tackle Garett Bolles had a tough time in the
      first half.  He had two holding penalties and was called for a
      third that was declined in the first half.  He was called for
      four for the game.  It didn't help that he was blocking Khalil Mack for most of the game.
    \item Charles Leno didn't want Bolles to feel
      lonely apparently because he come out after half time and got
      two quick holding penalties, himself.  
    \item Chris Harris had a big
      holding call near the goal line late in the third quarter.  The
      Bears got the touchdown on a David Montgomery run.  
    \item Eddie
      Goldman had a big penalty in the fourth quarter.  The call
      looked questionable.  The Bears forced a field goal anyway.
    \item Buster Skriene was off side on the conversion for the Broncos when they missed the kick.  That allowed the Broncos to go for two points and the win.  To top it off, they had 12 men in the huddle while driving for a field goal.
  \end{enumerate}

  \item Kyle Fuller had a huge interception in the fourth quarter with the Bears defense worn down and with their backs to the goal line.
  \item This was obviously could have been a tough loss.  The Bears defense wore down in the fourth quarter and it allowed the Broncos to drive the field not once but twice, the second time for the touchdown.  I don't think it would have made a difference but there will be plenty of people questioning whether playing in the preseason would have made gotten the defense in better shape.  I really , really doubt that 40 snaps or so would have made the difference.

    \begin{minipage}{1.0\linewidth}
      The Bears now avoid an 0-2 start and they won't face the uphill battle in the division against the now 2-0 Packers they could have.  But if they are going to compete, the offense has to come a live and score some points.  To do that, Mitch Trubusky has to complete every open pass.  This has to get better.
    \end{minipage}

  \end{enumerate}
\end{document}
