% Created 2019-02-17 Sun 09:59
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Tom Shannon}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Tom Shannon},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.1 (Org mode 9.1.9)}, 
 pdflang={English}}
\begin{document}

\subsection{Bunster Skrine is NOt a Downgrade.  But Is He a Permanent Solution?}
``How will \textbf{Buster Skrine} fit into the Bears defense to replace \textbf{Bryce Callahan}? A lot of fans have been calling him a downgrade. — @sam_gutterman

``Skrine projects to be a good fit. He didn’t have his best season last year with the Jets, but the struggles came mostly when he was forced to play on the outside because of injuries. Skrine has also been more durable than Callahan. He has missed a total of five games over the last three seasons but didn’t miss a single game in his first five seasons in the league. Durability was a knock on Callahan, who wound up getting more money from the Broncos than the Bears wanted to pay. I like the idea of adding a proven veteran at the nickel spot with Callahan departed. Skrine will be better than he was with the Jets because he has a much more talented pass rush in front of him.''
\end{quote}

I don't think many people locally are calling the addition of Skrine a downgrade.  Head coach \textbf{Matt Nagy} highlighted Skrine last year before the Bears played the Jets as one of their best players and its obvious that they signed him largely because of what they saw on tape in preparation for that game.

The one thing to keep in mind is that Skrine is 30 years old.  That means he might be a good fill in for a while but he's also not the future at that position.  The Bears drafted \textbf{Duke Shelly} out of Kansas State in the sixth round but I wouldn't hold my breath that he'll work out there as a starter.  Although he's reportedly a fine athlete, he's only 5'9''.  Admittedly you don't need the height playing nickel back that you do if you are playing on the outside but Shelly will still have to show that he can overcome that lack of height to cover taller receivers on the inside.

Losses of the Bryce Callahan-type are inevitable in the salary cap era of the NFL and as those types of losses go, Callahan isn't a huge one.  But I would say that the loss of Callahan did leave a hole on the defense long-term and that the Bears will be spending some time as they approach the draft for the next year or two looking for potential replacements.
\end{document}